{\new
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

{\bf {\dftbp}XT} is a general open source software package for \\[-0.6cm]
\begin{itemize}
\item fast atomistic electronic structure and molecular dynamics simulations
\item model and atomistic quantum transport at nanoscale 
\item many-body nonequilibrium phenomena
\item material and device modeling
\end{itemize}  

{\bf {\dftbp}XT} is an extended version of the {\bf{\dftbp}} code.
 
{\dftbpxt} package \cite{OpenSuite} is based on the {\dftbp} \cite{dftbp-paper,Pecchia_NJP} source code. Additionally, it suggests a number of new features, which are in the testing phase and may be included into the \dftbp release later. The extended functionality of \dftbpxt is mainly focused on many-body quantum transport and applications in nanoscience, material and device modeling. 
 
\null
In this version we present the following new features.

\begin{itemize}

\item Model Hamiltonians for transport calculations

We introduced the possibility to read model Hamiltonians from external data files and use it with or without a geometry structure. This is especially important for many-body quantum transport problems. See Sec.\,\ref{sec_model}.
  
\item Elastic dephasing

Two models of elastic dephasing ("B\"uttiker probe" and "vibronic dephasing") can be used now to include the dephasing and dissipation    beyond the coherent Green function method. Thus, we made a new step towards realistic material and device modeling. See Sec.\,\ref{sec_deph}. 
  
\item Application to STM spectroscopy

We added new options to simplify and make faster the calculation of currents for systems with changeable geometry (like the STM setup). We also supply the python scripts for modeling of the scanning process over tip position and voltage. See Sec.\,\ref{sec_stm}.

\end{itemize}

}